Causal inference is not a statistical problem

### 2023-03-03 manuscript.qmd
update data
add appendix

```{r}
n <- 100
set.seed(26775)

@@

set.seed(44433)

@@

>>>>

```{r}
n <- 100
set.seed(1331)

@@

set.seed(207052)

@@

## Appendix

R code to generate the tables and figures:

```{r}
#| eval: false
#| echo: true
library(tidyverse)
# devtools::install_github("LucyMcGowan/causalquartet")
library(causalquartet)

## Figure 2

ggplot(causalquartet, aes(x = x, y = y)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = "y ~ x") +
  facet_wrap(~type)

## Table 2

causalquartet %>%
  nest_by(type) %>%
  mutate(`Y ~ X` = round(coef(lm(y ~ x, data = data))[2], 2),
         `Y ~ X + Z` = round(coef(lm(y ~ x + z, data = data))[2], 2),
         `Correlation of X and Z` = round(cor(data$x, data$z), 2)) %>%
  select(-data, `Data generating mechanism` = type) %>%
  knitr::kable()
```
